Estimating duration in the presence of misclassification

### 2024-08-02 ATACCC.tex
Christl p78 comment
correct notation

From \cref{ATACCC:eq:di}, we can see that $d_i$ depends only on $i$'s random effects vector $\vec{\phi}_i$.
Therefore, the distribution of $d_i$ across the population of group $g$ is determined by $\vec{\phi}_i$'s mean, $\vec{\mu}_{\phi,g}$, and covariance matrix, $\matr{\Sigma}_\phi$.
% Hence, the uncertainty in the posterior distribution of the discretised duration cumulative distribution function for group $g$, $F_{D,g}(d) = \prob(D_i \leq d + 0.5)$ originate from the uncertainty in $\vec{\mu}_\phi$ and $\matr{\Sigma}_\phi$.

@@

A strength of the ATACCC data are its general population sample.
This is unlike most estimates (see \cref{E-intro:sec:previous-duration-estimates}) which are from hospitalised patients or healthcare workers.
This means that, notwithstanding the issues highlighted in the previous paragraph, the estimates are likely to be generalisable to the general population.

>>>>

From \cref{ATACCC:eq:di}, we can see that $d_i$ depends only on $i$'s random effects vector $\vec{\phi}_i$.
Therefore, the distribution of $d_i$ across the population of group $g(i)$ is determined by $\vec{\phi}_i$'s mean, $\vec{\mu}_{\phi,g(i)}$, and covariance matrix, $\matr{\Sigma}_\phi$.
% Hence, the uncertainty in the posterior distribution of the discretised duration cumulative distribution function for group $g$, $F_{D,g}(d) = \prob(D_i \leq d + 0.5)$ originate from the uncertainty in $\vec{\mu}_\phi$ and $\matr{\Sigma}_\phi$.

@@

A strength of the ATACCC data is its general population sample.
This is unlike most estimates (see \cref{E-intro:sec:previous-duration-estimates}) which are from hospitalised patients or healthcare workers.
This means that, notwithstanding the issues highlighted in the previous paragraph, the estimates are likely to be generalisable to the general population.
